Methods for Large Scale Learning to Rank

### 2014-11-20 report/Chapters/BenchmarkResults.tex
lessen van Dolf :)

>>>>

\section{Conclusions}
\label{chap:cross_comparison}
We have seen in the preceding sections that the evaluation of Learning to Rank methods is spread over several benchmark data sets. However, as the Learning to Rank methods evaluated differs between benchmarks, no single benchmark comparison can be regarded as a conclusive argument on which Learning to Rank method is most accurate. In the next chapter we will describe a meta-analysis based on a structured literature research that compares the ranking accuracy of Learning to Rank methods over multiple benchmark sets.\\

### 2014-11-20 report/Chapters/RelatedWork.tex
lessen van Dolf :)

>>>>

\section{Conclusions}
We have seen that a wide range of techniques for parallel and distributed computing are used in the field of parallel or distributed Learning to Rank. Only a small fraction of related work focusses on the MapReduce programming model, while MapReduce is the data processing framework of choice in industry \cite{Lin2013}. Furthermore we see that most related work that does involve MapReduce focusses either on distributed hyper-parameter optimisation \cite{Ganjisaffar2011} or on model optimisation techniques \cite{Long2012,Zinkevich2010}, while only one study describes a MapReduce implementation of a Learning to Rank algorithm itself \cite{Karimzadehgan2011}. This thesis provides an exploration of using MapReduce for parallel computation of Learning to Rank model training.
